\section{Orchestral Experience}

\subsection{Professional}
\denseouterlist{

    \entrybig[\textbullet]
    {\textbf{Sydney Symphony Orchestra}}{Sydney}
    {Regular casual double bassist, full time contract musician in 2014, 2015 and September 2017\textendash September 2018.}{2009\textendash current}

    \entrybig[\textbullet]
    {\textbf{Australian Chamber Orchestra}}{Sydney}
    {Regular casual double bassist.}{2013\textendash current}

    \entrybig[\textbullet]
    {\textbf{Opera Australia Orchestra}}{Sydney}
    {Regular casual double bassist.}{2016\textendash current}
    
    \entrybig[\textbullet]
    {\textbf{Click Track Music}}{Sydney}
    {Regular casual double bassist.}{2009\textendash current}

    \entrybig[\textbullet]
    {\textbf{Tasmanian Symphony Orchestra}}{Tasmania}
    {Casual double bassist.}{2013\textendash 2018}

    \entrybig[\textbullet]
    {\textbf{Auckland Philharmonia}}{Auckland}
    {Casual double bassist.}{2013}

    \entrybig[\textbullet]
    {\textbf{Ulster Orchestra}}{Belfast}
    {Held a trial for double bass section leader.}{Winter 2012}

}
\subsection{Training programs}
\denseouterlist{

    \entrybig[\textbullet]
    {\textbf{Emerging Artist}, Australian Chamber Orchestra}{Sydney}
    {Mentor: Maxime Bibeau.}{2013}
    
    \entrybig[\textbullet]
    {\textbf{Southbank Sinfonia}}{London}
    {Principal double bassist, twice appeared as a soloist.}{2011-2012}

    \entrybig[\textbullet]
    {\textbf{Sydney Symphony Fellowship}, Sydney Symphony Orchestra}{Sydney}
    {Also appeared with Sydney Sinfonia from 2008-2010.}{2010}

    \entrybig[\textbullet]
    {\textbf{Australian Youth Orchestra}}{Australia}
    {Double basss section player.}{2007\textendash 2008}

    \entrybig[\textbullet]
    {\textbf{Sydney Youth Orchestra}}{Sydney}
    {Principal double bassist, appeared as double bass soloist in 2006.}{2006\textendash 2008}


}
